---
title: "ABC Insurance - Case Study"
author: "Xiyun Zhou"
date: "2025-05-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

```

## R Markdown


```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(stringr)
library(gridExtra)
library(tidyr)
library(knitr)
library(scales)
```




 According to Bureau of statistics, 澳洲购买私人保险的人数。。。
 

```{r}
New <- read_excel("~/Desktop/Medibank /New Policies CY22_24 (1).xlsx")

End <- read_excel("~/Desktop/Medibank /Terminations CY22_24 (1).xlsx")

New$Age_Band <- factor(
  New$Age_Band,
  levels = c(
    "less than 30 Years",
    "30-39 Years",        
    "40-49 Years",        
    "50-59 Years",      
     "60+ Years"          
  )
)

End$Age_Band <- factor(
  End$Age_Band,
  levels = c(
    "less than 30 Years",
    "30-39 Years",        
    "40-49 Years",        
    "50-59 Years",      
     "60+ Years"          
  )
)

End$Tenure_Band <- factor(
  End$Tenure_Band,
  levels = c(
    "0 - 2 Years",
    "3 - 5 Years", 
   "6 - 10 Years",
   "11 - 19 Years",
   "20+ Years"
  )
)


New$Product <- factor(
  New$Product,
  levels = c(
    "Product A", "Product B","Product C", "Product D", "Product E", "Product F",
 "Product G", "Product H", "Other"
  )
)

End$Product <- factor(
  End$Product,
  levels = c(
    "Product A", "Product B","Product C", "Product D", "Product E", "Product F",
 "Product G", "Product H", "Other"
  )
)




head(New)
head(End)

na.omit(New)
na.omit(End)
```

```{r}
unique(New$Scale)
unique(New$Year)
unique(New$Age_Band)
unique(New$Product)
```

Total New and termination in 2022,2023,2024.


```{r}

new_policies_summary <- New%>%
  group_by(Year) %>%
  summarise(Total_New = sum(`New Policies`, na.rm = TRUE)) %>% 
  mutate(New_K = Total_New/ 1000)
  


ggplot(new_policies_summary, aes(x = Year, y = New_K, fill = as.factor(Year))) +
  geom_bar(stat = "identity", width = 0.4) +  
  geom_line(group = 1, color = "black", size = 1) +
  geom_point(color = "black", size = 2) +
  scale_x_continuous(breaks = c(2022, 2023, 2024)) +  # Only show full years on x-axis
  geom_text(aes(label = round(New_K, 1)), vjust = -0.3, size = 5) + 
  labs(title = "Total New Policies by Year",
       x = "Year", y = "Total Number of New Policies (in thousands") +
  theme_minimal() +
  theme(legend.position = "none")  
```
```{r}
new_policies_summary <- New %>%
  group_by(Year) %>%
  summarise(Total_New = sum(`New Policies`, na.rm = TRUE)) %>%
  mutate(New_K = Total_New / 1000)

New_p1 <- ggplot(new_policies_summary, aes(x = Year, y = New_K, fill = as.factor(Year))) +
  geom_line(aes(group = 1), color = "#B22222",, size = 1) +
  geom_point(color = "black", size = 2) +
  geom_text(aes(label = round(New_K, 1)), nudge_y = 7, size = 5) +
  scale_x_continuous(breaks = c(2022, 2023, 2024)) +
  scale_y_continuous(limits = c(600, 780), expand = expansion(mult = c(0, 0.05))) +
  labs(
    title = "Total New Policies by Year",
    x = "Year",
    y = "Total New Policies (in thousands)"
  ) +
  theme_minimal() +
  theme(legend.position = "none")


```







Percentage change

```{r}
new_policies_summary <- new_policies_summary %>%
  arrange(Year)

# Calculate percentage change from previous year
new_policies_summary <- new_policies_summary %>%
  mutate(Percent_Change = (Total_New/ lag(Total_New) - 1) * 100)

ggplot(new_policies_summary, aes(x = Year, y = Percent_Change, fill = Percent_Change > 0)) +
  geom_bar(stat = "identity", width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = paste0(round(Percent_Change, 1), "%")), vjust = -0.5, size = 5) +
  scale_fill_manual(values = c("TRUE" = "green", "FALSE" = "red")) +
  labs(title = "Year-over-Year % Change in New Policies",
       x = "Year", y = "Percentage Change (%)") +
  theme_minimal()
```






```{r}
terminations_summary <- End %>%
  group_by(Year) %>%
  summarise(Total_Terminations = sum(Terminations, na.rm = TRUE))

ggplot(terminations_summary, aes(x = Year, y = Total_Terminations, fill = as.factor(Year))) +
  geom_bar(stat = "identity", width = 0.4) +
  geom_line(group = 1, color = "black", size = 1) +
  geom_point(color = "black", size = 2) +
  scale_x_continuous(breaks = c(2022, 2023, 2024)) + 
  geom_text(aes(label = Total_Terminations), vjust = -0.3, color = "black", size = 4) + 
  labs(title = "Total Terminations by Year",
       x = "Year", y = "Total Number of Terminations") +
  theme_minimal() +
  theme(legend.position = "none")


ggplot(terminations_summary, aes(x = Year, y = Total_Terminations))+
  scale_x_continuous(breaks = c(2022, 2023, 2024)) + 
  geom_line()

```


```{r}
terminations_summary <- terminations_summary %>%
  arrange(Year) %>%
  mutate(Percent_Change = (Total_Terminations / lag(Total_Terminations) - 1) * 100)

# Plot percent change
ggplot(terminations_summary, aes(x = Year, y = Percent_Change)) +
  geom_bar(stat = "identity", fill = "tomato") +
  geom_text(aes(label = paste0(round(Percent_Change, 1), "%")), vjust = -0.5, size = 5) +
  labs(title = "Year-over-Year % Change in Terminations",
       x = "Year", y = "Percentage Change (%)") +
  theme_minimal()
```


```{r}
terminations_summary <- terminations_summary %>%
  mutate(Terminations_K = Total_Terminations / 1000)

Term_p1<- ggplot(terminations_summary, aes(x = Year, y = Terminations_K)) +
  geom_line(aes(group = 1), color = "steelblue", size = 1) +
  geom_point(color = "black", size = 2) +
 geom_text(aes(label = round(Terminations_K, 1)), nudge_y = 8, size = 5) +
  scale_y_continuous(limits = c(600, 780), expand = expansion(mult = c(0, 0.05)))+
  scale_x_continuous(breaks = c(2022, 2023, 2024)) +
  labs(title = "Total Terminations by Year",
       x = "Year", y = "Terminations (in Thousands)") +
  theme_minimal() +
  theme(legend.position = "none")

grid.arrange(New_p1, Term_p1, nrow = 2)
```

```{r}
# Assuming you have: new_policies_summary and termination_summary
net_summary <- full_join(new_policies_summary, terminations_summary, by = "Year") %>%
  mutate(Net_Gain = Total_New - Total_Terminations)

ggplot(net_summary, aes(x = Year, y = Net_Gain, fill = Net_Gain > 0)) +
  geom_bar(stat = "identity", width = 0.4, show.legend = FALSE) +
  scale_x_continuous(breaks = c(2022, 2023, 2024)) + 
  geom_text(aes(label = format(Net_Gain, big.mark = ",")), vjust = -0.5, size = 5) +
  
  scale_fill_manual(values = c("TRUE" = "steelblue", "FALSE" = "firebrick")) +
  labs(title = "Net Policy Gain/Loss by Year",
       x = "Year", y = "Net Gain (New Policies - Terminations)") +
  theme_minimal()

```
*By State 

```{r}

new_by_state <- New%>%
  group_by(State) %>%
  summarise(`New Policies`= sum(`New Policies`, na.rm = TRUE))

term_by_state <- End %>%
  group_by(State) %>%
  summarise(Terminations = sum(Terminations, na.rm = TRUE))

# Combine into one table
state_summary <- full_join(new_by_state, term_by_state, by = "State") %>%
  mutate(Net_Gain = `New Policies` - Terminations)



state_long <- state_summary %>%
  pivot_longer(cols = c(`New Policies`, Terminations),
               names_to = "Type", values_to = "Count")

ggplot(state_long, aes(x = State, y = Count, fill = Type)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "New Policies vs Terminations by State",
       y = "Number of Policies") +
  theme_minimal()


ggplot(state_summary, aes(x = State, y = Net_Gain, fill = Net_Gain > 0)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  scale_fill_manual(values = c("TRUE" = "steelblue", "FALSE" = "firebrick")) +
  labs(title = "Net Policy Gain/Loss by State",
       y = "Net Policies (New - Terminations)") +
  theme_minimal()
```

Plot 1: New Policies vs Terminations by State
NSW & VIC: Very high volume on both acquisition and termination → large markets, but very competitive.
VIC, TAS, SA, NSW all show large net losses

VIC is the worst, largest net loss

Potential factors:

Highly competitive market with aggressive poaching

Poor retention strategies or product dissatisfaction


WA is the only strong positive performer: net gain > 90,000
WA (Strong performer)
May have:

Better regional pricing or product-market fit

Fewer competitors

Strong brand presence or partnerships in WA

Lower price sensitivity / more loyal members





# 目标客户群体， segment 




```{r}

New_summary <- New%>%
  group_by(Age_Band,Year) %>%
  summarise(Total_New_Policies = sum(`New Policies`, na.rm = TRUE)) %>% 
  mutate(Policies_Thousands = Total_New_Policies / 1000)



New_age <- ggplot(New_summary, aes(x = Age_Band, y = Policies_Thousands, fill = as.factor(Year))) +
  geom_bar(stat = "identity",  position = "dodge") + 
  labs(title = "New Policies by Age Band", x = "Age Band", y = "Number of New Policies (in thousands)",
        fill = "Year") +
  theme_minimal()


 Terminations_summary <- End%>%
  group_by(Age_Band,Year) %>%
  summarise(Total_Terminations= sum(`Terminations`, na.rm = TRUE)) %>% 
  mutate(Terminations_Thousands = Total_Terminations / 1000)


End_age <- ggplot(Terminations_summary, aes(x = Age_Band, y = Terminations_Thousands, fill = as.factor(Year))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Terminations by Age Band", x = "Age Band", y = "Number of Terminations (in thousands)",
       fill = "Year") +
  theme_minimal()

grid.arrange(New_age, End_age, ncol = 2)



```
# Average 



```{r}
Terminations_summary_avg <- End %>%
  group_by(Age_Band) %>%
  summarise(Average_Terminations = mean(Terminations, na.rm = TRUE)) %>%
  mutate(Terminations_Thousands = Average_Terminations / 1000)

# Step 2: Create the bar plot
End_age_avg <- ggplot(Terminations_summary_avg, aes(x = Age_Band, y = Terminations_Thousands, fill = Age_Band)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Terminations by Age Band (2022–2024)",
       x = "Age Band",
       y = "Average Number of Terminations (in thousands)") +
  theme_minimal() +
  theme(legend.position = "none")  # Remove legend if fill is self-explanatory

End_age_avg


grid.arrange(New_age_avg, End_age_avg, ncol = 2)
```

```{r}

New_avg <- New %>%
  group_by(Age_Band, Year) %>%
  summarise(Total_New = sum(`New Policies`, na.rm = TRUE)) %>%
  group_by(Age_Band) %>%
  summarise(Average_New_Policies = mean(Total_New)) %>%
  mutate(Metric = "New Policies", Value = Average_New_Policies / 1000)

# Step 2: Total terminations per Age Band per Year, then average
End_avg <- End %>%
  group_by(Age_Band, Year) %>%
  summarise(Total_Terminations = sum(Terminations, na.rm = TRUE)) %>%
  group_by(Age_Band) %>%
  summarise(Average_Terminations = mean(Total_Terminations)) %>%
  mutate(Metric = "Terminations", Value = Average_Terminations / 1000)


# Step 3: Combine both into one tidy dataframe
Combined_avg <- bind_rows(
  New_avg %>% select(Age_Band, Metric, Value),
  End_avg %>% select(Age_Band, Metric, Value)
)

# Step 4: Plot
Combined_plot <- ggplot(Combined_avg, aes(x = Age_Band, y = Value, fill = Metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Average New Policies vs Terminations by Age Band (2022–2024)",
       x = "Age Band",
       y = "Average Number of Policies (in thousands)",
       fill = "") +
  theme_minimal()

Combined_plot



```




```{r}

New_product <- New%>%
  group_by(Product, Year) %>%
  summarise(Total_New_Policies = sum(`New Policies`, na.rm = TRUE)) %>% 
  mutate(Policies_Thousands = Total_New_Policies / 1000)

New_p <- ggplot(New_product, aes(x = Product, y = Policies_Thousands, fill = as.factor(Year))) +
   geom_bar(stat = "identity", position = "dodge") +
  labs(title = "New Policies by Product and Year",
       x = "Product", y = "Number of New Policies (in thousands)",
       fill = "Year") +
  theme_minimal()

End_product <- End%>%
  group_by(Product, Year) %>%
  summarise(Total_End_Policies = sum(Terminations, na.rm = TRUE)) %>% 
  mutate(Policies_Thousands = Total_End_Policies / 1000)


End_p <- ggplot(End_product, aes(x = Product, y = Policies_Thousands, fill = as.factor(Year))) +
   geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Terminations by Product and Year", x = "Product", y = "Number of Terminations (in thousands)", fill = "Year") +
  theme_minimal()

grid.arrange(New_p, End_p, ncol = 2)


# Net gain/loss 

```

```{r}

# Step 1: Average New Policies by Product
New_product_avg <- New %>%
  group_by(Product, Year) %>%
  summarise(Total_New = sum(`New Policies`, na.rm = TRUE)) %>%
  group_by(Product) %>%
  summarise(Average_New_Policies = mean(Total_New)) %>%
  mutate(Metric = "New Policies", Value = Average_New_Policies / 1000)

# Step 2: Average Terminations by Product
End_product_avg <- End %>%
  group_by(Product, Year) %>%
  summarise(Total_End = sum(Terminations, na.rm = TRUE)) %>%
  group_by(Product) %>%
  summarise(Average_Terminations = mean(Total_End)) %>%
  mutate(Metric = "Terminations", Value = Average_Terminations / 1000)

# Step 3: Combine both into one tidy dataset
Combined_product_avg <- bind_rows(
  New_product_avg %>% select(Product, Metric, Value),
  End_product_avg %>% select(Product, Metric, Value)
)

# Step 4: Plot the comparison
Product_comparison_plot <- ggplot(Combined_product_avg, aes(x = Product, y = Value, fill = Metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Average New Policies vs Terminations by Product (2022–2024)",
       x = "Product",
       y = "Average Number of Policies (in thousands)",
       fill = "") +
  theme_minimal()

Product_comparison_plot
```

```{r}
target_products <- c("Product A", "Product C", "Product D", "Product G")
product_scale_summary <- End %>%
  filter(Product %in% target_products) %>%
  group_by(Product, Scale) %>%
  summarise(Total_End = sum(Terminations, na.rm = TRUE)) %>%
  group_by(Product) %>%
  mutate(Percent = round(Total_End / sum(Total_End) * 100, 1))

# Create one pie chart per product using facet_wrap
pie_chart_product <- ggplot(product_scale_summary, aes(x = "", y = Percent, fill = Scale)) +
  geom_col(width = 1, color = "white") +
  coord_polar("y") +
  facet_wrap(~ Product) +
  geom_text(aes(label = paste0(Percent, "%")),
            position = position_stack(vjust = 0.5), size = 3) +
  labs(title = "Customer Scale Breakdown for Key Products",
       x = NULL, y = NULL, fill = "Policy Scale") +
  theme_void() +
  theme(strip.text = element_text(face = "bold"))

pie_chart_product
```










Product A – Strong Performer (Growing Leader)
New Policies: High and growing steadily (especially 2024).

Terminations: Also increasing, but at a much lower rate than acquisitions.

✅ Net Positive Growth → Product A is your top acquisition product with healthy retention.

Product C – Underperformer (Critical Issue)
New Policies: Near-zero acquisition across all years.

Terminations: Fairly high and increasing.

Severe Net Loss

signal:

Outdated pricing or uncompetitive coverage

Customer dissatisfaction

Poor market targeting

Product D,F,G  – Shrinking Interest
New Policies: Strong in 2022, dropped by 2024.

Terminations: Stayed consistently high.

Negative trajectory → Possibly losing appeal or being replaced by newer alternatives.

Product D F G keep loss customer, with rarely acquisition in 2024. 


```{r}

New %>% filter(Product == "Product C") 

```




```{r}
age_product_table <- table(New$Age_Band, New$Product)

age_product_table


```

# Percentage 

```{r}
Product_Scale <- ggplot(New, aes(x = Scale, fill = Product)) +
  geom_bar(position = "dodge") +
  labs(title = "New Policies by Scale and Product",
       x = "Scale", y = "Number of New Policies") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 


Product_Age <- ggplot(New, aes(x = Age_Band, fill = Product)) +
  geom_bar(position = "dodge") +
  labs(title = "New Policies by Age band and Product",
       x = "Scale", y = "Number of New Policies") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

grid.arrange(Product_Scale, Product_Age, ncol = 2)

```
# Both charts (Scale by Product & Age Band by Product) reveal that:

Most products share very similar distribution patterns of customers across different scales (Single, Couple, etc.) and age bands.

There's no clear targeting strategy visible — e.g., Product A, B, C, D all attract similar proportions of Singles, Families, 30–49 year-olds, etc.

Even “Other” products dominate across all segments, diluting unique product segmentation.

 Lack of Product Differentiation,  Differentiation	The products may not be tailored to specific customer needs (e.g., Product C isn’t clearly appealing to any unique demographic).
 
 Missed Segmentation Opportunities, There’s likely room to design products more targeted to, say, young singles, senior couples, or single parents.


Product Positioning Strategy Review:

Audit the product features vs. demographic needs.

Cluster customer profiles and match with tailored benefits.

Reposition underperforming products or consolidate overlapping ones.

Launch pilot offerings for underserved segments (e.g., tailored plans for seniors or young couples with extras focus).


# 
By policy type 








```{r}
new_pie_data <- New %>%
  group_by(Year, Scale) %>%
  summarise(Total = sum(`New Policies`), .groups = "drop") %>%
  group_by(Year) %>%
  mutate(Percent = Total / sum(Total) * 100,
         Label = paste0(Scale, "\n", round(Percent, 1), "%"))


ggplot(new_pie_data, aes(x = "", y = Percent, fill = Scale)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  facet_wrap(~Year) +
   geom_text(aes(label = Label),
            position = position_stack(vjust = 0.5),
            size = 2, color = "white") +
  labs(title = "New Policy Distribution by Scale",
       fill = "Policy Scale") +
  theme_void() +  # remove axes
  theme(strip.text = element_text(size = 12, face = "bold"))

```
```{r}
end_pie_data <- End %>%
  group_by(Age_Band) %>%
  summarise(Term_avg = mean(Terminations, na.rm = TRUE), .groups = "drop") %>%
  mutate(Percent = Term_avg / sum(Term_avg) * 100,
         Label = paste0(Age_Band, "\n", round(Percent, 1), "%"))


ggplot(end_pie_data, aes(x = "", y = Percent, fill = Age_Band)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
   geom_text(aes(label = Label),
            position = position_stack(vjust = 0.5),
            size = 3, color = "white") +
  labs(title = "Terminations Distribution by Age Band",
       fill = "Policy Scale") +
  theme_void() +  # remove axes
  theme(strip.text = element_text(size = 12, face = "bold"))
```


```{r}



```


```{r}

unique(End$Tenure_Band)

unique(End$Next_Health_Fund)
```

Assumption: 年轻人更容易离开（多变）， 
Tenure period 越长越不容易离开。 


```{r}
filter_End <- End %>% 
  filter(`Next_Health_Fund` != "Dropped Private Health Insurance")


bubble_data <- filter_End %>%
  group_by(Tenure_Band, Age_Band) %>%
  summarise(Total_Terminations = sum(Terminations, na.rm = TRUE)) %>%
  ungroup()

# Optional: calculate churn rate if you have policy base (e.g., Total_Customers)
# bubble_data <- bubble_data %>%
#   mutate(Churn_Rate = Total_Terminations / Total_Customers)

# Step 2: Create the bubble plot
ggplot(bubble_data, aes(x = Tenure_Band, y = Age_Band, size = Total_Terminations, fill = Age_Band)) +
  geom_point(alpha = 0.7, shape = 21, color = "black") +
  scale_size_continuous(name = "Terminations", range = c(3, 15)) +
  labs(title = "Terminations by Tenure Band and Age Band",
       x = "Tenure Band", y = "Age Band") +
  theme_minimal() +
  theme(legend.position = "right")

```

```{r}

# Step 1: Convert Tenure Band into ordered numeric values
tenure_order <- c("0 - 2 Years", "3 - 5 Years", "6 - 10 Years", "11 - 19 Years", "20+ Years")
End$Tenure_Band <- factor(End$Tenure_Band, levels = tenure_order, ordered = TRUE)
End$Tenure_Num <- as.numeric(End$Tenure_Band)

# Step 2: Summarise total terminations by Tenure_Num
cor_data <- End %>%
  group_by(Tenure_Num) %>%
  summarise(Total_Terminations = sum(Terminations, na.rm = TRUE))

# Step 3: Correlation plot
ggplot(cor_data, aes(x = Tenure_Num, y = Total_Terminations)) +
  geom_point(size = 4, color = "#2a9d8f") +
  geom_smooth(method = "lm", se = FALSE, color = "#264653", linetype = "dashed") +
  labs(title = "Correlation Between Tenure and Terminations",
       x = "Tenure Band (numeric scale)",
       y = "Total Terminations") +
  theme_minimal()



```

```{r}
# Order tenure band correctly
tenure_order <- c("0 - 2 Years", "3 - 5 Years", "6 - 10 Years", "11 - 19 Years", "20+ Years")
End$Tenure_Band <- factor(End$Tenure_Band, levels = tenure_order, ordered = TRUE)

# Summarise average terminations per tenure band
tenure_summary <- End %>%
  #filter(`Next_Health_Fund` != "Dropped PHI") %>%  # Optional: focus on switching
  group_by(Tenure_Band) %>%
  summarise(Avg_Terminations = mean(Terminations, na.rm = TRUE))

# Plot
ggplot(tenure_summary, aes(x = Tenure_Band, y = Avg_Terminations, group = 1)) +
  geom_line(color = "#1f77b4", size = 1.2) +
  geom_point(color = "#1f77b4", size = 3) +
  labs(title = "Average Terminations by Tenure Band (2022–2024)",
       x = "Tenure Band",
       y = "Average Terminations") +
  theme_minimal()
```









```{r}
new_sources <- New %>%
  filter(!is.na(Previous_Health_Fund)) %>%
  group_by(Previous_Health_Fund) %>%
  summarise(Customers_From = sum(`New Policies`)) %>%
  arrange(desc(Customers_From))

ggplot(head(new_sources, 5), aes(x = reorder(Previous_Health_Fund, Customers_From), y = Customers_From)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 5 Funds Customers Came From", x = "Previous Fund", y = "New Customers") +
  theme_minimal()


churn_targets <- End%>%
  filter(!is.na(Next_Health_Fund)) %>%
  group_by(Next_Health_Fund) %>%
  summarise(Customers_To = sum(Terminations)) %>%
  arrange(desc(Customers_To))

ggplot(head(churn_targets, 5), aes(x = reorder(Next_Health_Fund, Customers_To), y = Customers_To)) +
  geom_bar(stat = "identity", fill = "firebrick") +
  coord_flip() +
  labs(title = "Top 5 Funds Customers Switched To", x = "Next Fund", y = "Terminated Customers") +
  theme_minimal()

```
# Net Gain/loss of competitors analysis 

```{r}
# Summarise new customers by previous health fund
new_sources <- New %>%
  filter(!is.na(Previous_Health_Fund)) %>%
  group_by(Fund = Previous_Health_Fund) %>%
  summarise(New_Customers = sum(`New Policies`, na.rm = TRUE))

# Summarise terminated customers by next health fund
churn_targets <- End %>%
  filter(!is.na(Next_Health_Fund)) %>%
  group_by(Fund = Next_Health_Fund) %>%
  summarise(Terminated_Customers = sum(Terminations, na.rm = TRUE))

# Combine datasets
net_fund_flow <- full_join(new_sources, churn_targets, by = "Fund") %>%
  mutate(
    New_Customers = replace_na(New_Customers, 0),
    Terminated_Customers = replace_na(Terminated_Customers, 0),
    Net_Change = New_Customers - Terminated_Customers
  ) %>%
  arrange(desc(Net_Change))

# Plot top 5 gain/loss funds
top_funds <- net_fund_flow %>%
  slice_max(abs(Net_Change), n = 10)

ggplot(top_funds, aes(x = reorder(Fund, Net_Change), y = Net_Change, fill = Net_Change > 0)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_manual(values = c("TRUE" = "steelblue", "FALSE" = "firebrick"),
                    labels = c("Loss", "Gain")) +
  scale_y_continuous(labels = label_number(scale = 1/1000, suffix = "K")) + 
  labs(
    title = "Competitive Positioning: Net Policy Gain/Loss",
    x = "Fund",
    y = "Net Gain/Loss (New - Terminated)",
    fill = "Result"
  ) +
  theme_minimal()
```







# Action



